Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-18 vesicle_code/docs/permeableVes/main.tex
adjusted line size and created stenosis in pdf format
yny

We consider both an impermeable and semi-permeable vesicle
with initial reduced area $\alpha = 0.65$ passing through a constricted
geometry and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
The impermeable case agrees with experimental
results in Figure 3 of \cite{abk-fai-sto2006}, and the results indicate
that less excess pressure is required to maintain a constant flow rate when the
vesicle is semi-permeable. Our simulations indicate the
semi-permeability does affect the excess pressure, and the vesicle's
reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced area
decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).

>>>>

We consider both an impermeable and semi-permeable vesicle
with initial reduced area $\alpha = 0.65$ passing through a long narrow channel
and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
The impermeable case agrees with experimental
results in Figure 3 of \cite{abk-fai-sto2006}, and the results indicate
that less excess pressure is required to maintain a constant flow rate when the
vesicle is semi-permeable. First we note that the vesicle deflates from the beginning due to the high flow velocity, consistent with the results for a vesicle in a Poiseuille flow in open space. {\bf YNY: What is the flow velocity in the inlet/outlet? need to specify these to make connection to the phase diagram in the Poiseuille flow section.}
As the vesicle enters the stenosis channel, the vesicle continues to deflate in the front even though we observe influx (red segment) at various rear locations in the membrane. 
These results are consistent with the results in \cite{Pak2015_PNAS} where the membrane tension is sufficiently large in the front of the vesicle as it goes through a constrictive channel.

Our simulations indicate the
semi-permeability does affect the excess pressure, and the vesicle's
reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced area
decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
